---
title: Google Cloud & NCAA® ML Competition 2018-Women's 
author: "Pranjal Vijay"
date: "March 6, 2018"
output: html_document
---

### Loading the libraries
```{r}

library(caret)
library(readr)
library(dplyr)
library(magrittr)
library(ModelMetrics)
library(ggplot2)
library(stats)
```

### Loading the WNCAATouneyCompactResults Data

```{r}
WNCAAT_result <- read.csv("C:/Users/ddddd/Comptitions/Kaggle/Google Cloud & NCAA/WNCAATourneyCompactResults.csv",stringsAsFactors = FALSE)

```

### Research question
We are already given a research question by this competition on Kaggle itself.

Stage 1 - You should submit predicted probabilities for every possible matchup in the past 4 NCAA® tournaments (2014-2017).

### DAta Exploration

```{r}
names(WNCAAT_result)
```
```{r}
str(WNCAAT_result)
```


### Data Preprocessing

```{r}
WNCAAT_result %>% 
  filter( Season != "NA", DayNum != "NA", WTeamID != "NA", WScore != "NA", LTeamID != "NA", LScore != "NA", NumOT != "NA") %>%
  select(Season, DayNum, WTeamID, WScore , LTeamID, LScore, NumOT) %>% 
  group_by(DayNum, WTeamID, WScore , LTeamID, LScore, NumOT) %>% 
  summarise(count=n())
```


#### As asked for stage 1, I filterized the data for season 2013 to 2017

```{r}
WNCAAT_result %>% 
  filter(Season >= 2013, Season != "NA", DayNum != "NA", WTeamID != "NA", WScore != "NA", LTeamID != "NA", LScore != "NA",  NumOT != "NA") %>%
  select(Season,DayNum, WTeamID, WScore , LTeamID, LScore, NumOT) %>% 
  #mutate(Seasons = Season >= 2013 )
  group_by(DayNum, WTeamID, WScore , LTeamID, LScore, NumOT) %>% 
  summarise(count=n())
```


#### Normalization & Data Partitioning
```{r}
normalize <- function(WNCAAT_result) {
 return ((WNCAAT_result - min(WNCAAT_result)) / (max(WNCAAT_result) - min(WNCAAT_result)))
}
inTrain <- createDataPartition(y=WNCAAT_result$WTeamID,
                              p=0.90, list=FALSE)
training <- WNCAAT_result[inTrain,]
testing <- WNCAAT_result[-inTrain,]

dim(training)
dim(testing)
```

### Modelling

```{r}
 m <- model.matrix( 
  ~ WScore  + LScore + Season + DayNum  + WScore + LTeamID + LScore + NumOT+WTeamID,
  data = training )
 
training <- data.frame(training, m)

glm_model <- glm(WTeamID ~ WScore  + LScore + Season + DayNum  + WScore + LTeamID + LScore + NumOT,
                 data = training)
summary(glm_model)
```


### Neural network 

```{r}
form <- as.formula(glm_model)

```

```{r}
library(nnet)
library(neuralnet)
#_nnet <- nnet(form, data=training, size=4, MaxNWts=100)

Solution<- neuralnet(form, data=training , hidden=c(5,5), linear.output=FALSE,  threshold=0.0000001)

#Predictions
prediction(Solution)

plot(Solution)
```
