---
title: Google Cloud & NCAA® ML Competition 2018-Women's

author: "Pranjal Vijay"
date: "March 6, 2018"
output: html_document
---

###Loading the required libraries

```{r}

library(caret)
library(readr)
library(dplyr)
library(magrittr)
library(ModelMetrics)
library(ggplot2)
library(stats)
```

### Loading the WNCAATouneyCompactResults Data
```{r}
WNCAAT_result <- read.csv("C:/Users/ddddd/Comptitions/Kaggle/Google Cloud & NCAA/WNCAATourneyCompactResults.csv",stringsAsFactors = FALSE)

```

### Research question for stage 1
We are already given a research question by this competition on Kaggle itself.

Stage 1 - You should submit predicted probabilities for every possible matchup in the past 4 NCAA® tournaments (2014-2017).

### Data Exploration

```{r}
names(WNCAAT_result)
```
```{r}
str(WNCAAT_result)
```
```{r}
WNCAAT_result$WLoc <- as.factor(WNCAAT_result$WLoc )
```
```{r}
str(WNCAAT_result)
```


### Data Preprocessing
```{r}
WNCAAT_result %>% 
  filter( Season != "NA", DayNum != "NA", WTeamID != "NA", WScore != "NA", LTeamID != "NA", LScore != "NA", WLoc != "NA", NumOT != "NA") %>%
  select(Season, DayNum, WTeamID, WScore , LTeamID, LScore, WLoc, NumOT) %>% 
  group_by(Season,DayNum, WTeamID, WScore , LTeamID, LScore, WLoc, NumOT) %>% 
  summarise(count=n())
```


#### As asked for stage 1, I filterized the data for season 2013 to 2017
```{r}
WNCAAT_result %>% 
  filter(Season >= 2013, Season != "NA", DayNum != "NA", WTeamID != "NA", WScore != "NA", LTeamID != "NA", LScore != "NA", WLoc != "NA", NumOT != "NA") %>%
  select(Season,DayNum, WTeamID, WScore , LTeamID, LScore, WLoc, NumOT) %>% 
  #mutate(Seasons = Season >= 2013 )
  group_by(Season, DayNum, WTeamID, WScore , LTeamID, LScore, WLoc, NumOT) %>% 
  summarise(count=n())
```


### Data Partitioning for training and testing
```{r}
inTrain <- createDataPartition(y=WNCAAT_result$WTeamID,
                              p=0.90, list=FALSE)
training <- WNCAAT_result[inTrain,]
testing <- WNCAAT_result[-inTrain,]
dim(training)
dim(testing)
```

### Modelling
```{r}
WNCAAT_Model = lm(WTeamID ~  Season+ WScore  + LScore +DayNum , data = training)
summary(WNCAAT_Model)
```

Here we get 74% accuracy and p value <0.05 

### Prediction

```{r}
WNCAAT_Model_Pred <- predict(WNCAAT_Model, testing)

plot(WNCAAT_Model_Pred)
```





